Contextual Combinatorial Cascading Bandits

### 2015-12-20 contextual combinatorial cascading bandits.tex
revise proof outline

	Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}
	Then we need to bound $f(A, \bU_t)$ and $f_{\wedge}(A, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$. First we have the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing.
	\begin{lemma}
		\CLemmaIncre
	\end{lemma}
	Then we have an estimate of the expected reward with UCB $\bU_t$.
	\begin{lemma}
		\CLemmaTech
	\end{lemma}
	Next we only need to estimate $\det(\bV_t)$ and those contextual information of observed base arms in $\bV$-norms.
	\begin{lemma}
		\CLemmaSumXiEstimateInDet
	\end{lemma}
	\begin{lemma}
		\CLemmaDetVt
	\end{lemma}
	Then it is easy to derive the proof.
\end{proof}

@@

	Then by Lemma \ref{lem:estimateTech},
	\begin{equation} \label{eq:btuttrue}
		f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
	\end{equation}
	Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
	\begin{align}
		R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
		& \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
	\end{align}
	Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
	\begin{align*}
		&\EE_t[R_{\wedge}(t, \bA_t)] \\
		\leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
		\leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
	\textbf{lem:DeltaEsimateWithP*}\end{align*}
\end{proof}

@@

	For the disjunctive case, we have
	\begin{align}
		&R(T) = \EE \left[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \right] \notag\\
		&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
		&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
		&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
		&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
		& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
		&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
		&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMdetEst}
	\end{align}
	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\beta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.

>>>>

	Then we use a prefix to replace $\bA_t$ such that the probability of observing all items is close to $f_{\wedge}^{\ast}$ and the gaps are close to those of the original solutions.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}
	Then we use the prefix to replace $\bA_t$ to compute the expected regret. Next we need to show the expected reward function is increasing with respect to $w$ when $\gamma~s$ are decreasing and $\gamma's$ are increasing and bound $f(\bA_t, \bU_t)$ and $f_{\wedge}(\bB_t, \bU_t)$ which is non-linear and contains discounted parameters $\gamma$.
	\begin{lemma}
		\CLemmaIncre
	\end{lemma}
	\begin{lemma}
		\CLemmaTech
	\end{lemma}
	From the above Lemmas, the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next two Lemmas solve this issue.
	\begin{lemma}
		\CLemmaSumXiEstimateInDet
	\end{lemma}
	\begin{lemma}
		\CLemmaDetVt
	\end{lemma}
	Then we can use a mean inequality to derive the result.
\end{proof}

@@

	Then by Lemma \ref{lem:estimateTech},
	\begin{equation} \label{eq:btuttrue}
		f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\bbeta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
	\end{equation}
	Therefore, combining Eq.\eqref{eq:andstarbt} and \eqref{eq:btuttrue}, we have
	\begin{align}
		R_{\wedge}(t, \bB_t) & = f_{\wedge, t}^{\ast} - f_{\wedge}(\bB_t, \theta_{\ast}^{\top}x_t) \nonumber \\
		& \leq \sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}. \label{eq:sumbetax}
	\end{align}
	Finally from Inequalities~\eqref{eq:btOneotbt} and \eqref{eq:sumbetax}， we can derive the result
	\begin{align*}
		&\EE_t[R_{\wedge}(t, \bA_t)] \\
		\leq& \frac{8}{f_{\wedge, t}^*} \EE \left[\bOne\{ \bO_t \geq \abs{\bB_t} \}\sum_{k=1}^{\abs{\bB_t}}\bbeta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right]\\
		\leq& \frac{8}{f_{\wedge}^*} \EE \left[ \sum_{k=1}^{ \bO_t } \bbeta_{t-1}(\delta) \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
	\end{align*}
\end{proof}

@@

	For the disjunctive case, we have
	\begin{align}
		&R(T) = \EE \left[\sum_{t=1}^{T} \EE_{t}[R(t, \bA_t)] \right] \notag\\
		&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \EE_t \left[\bbeta_{t-1}(\delta) \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMdeltaEst}\\
		&\leq \EE\left[\sum_{t=1}^{T} \frac{1}{p^*} \bbeta_{T}(\delta) \EE_t \left[ \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}\right] \right] \label{eq:pfMbeta}\\
		&\leq \EE \left[\frac{1}{p^*} \bbeta_T(\delta) \sqrt{\left(\sum_{t=1}^{T} \bO_t\right) \left( \sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2 \right)} \right ]  \label{eq:pfMmeanEq}\\
		&\leq \EE\left[\frac{1}{p^*} \left( \sqrt{ \ln \left( \frac{\det(\bV_T)}{\lambda^d \delta^2} \right)} + \sqrt{\lambda} \right) \right. \notag\\
		& \left. \qquad \qquad \cdot \sqrt{TK \cdot 2\ln \left(\frac{\det(\bV_T)}{\lambda^d} \right)} \right] \label{eq:pfMsumXi}\\
		&\leq \frac{\sqrt{2}}{p^*} \left(\sqrt{ d \ln \left( \frac{1 + C_\gamma T/(\lambda d)}{\delta^{2/d}} \right) } + \sqrt{\lambda} \right) \notag\\
		&\qquad \qquad \cdot \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}. \label{eq:pfMdetEst}
	\end{align}
	Inequality \eqref{eq:pfMdeltaEst} is by Lemma \ref{lem:DeltaEsimateWithP*}. 
	Inequality \eqref{eq:pfMbeta} is because $\bbeta_{t}(\delta)$ is increasing with respect to $t$, derived by the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:detVt}. 
	Inequality \eqref{eq:pfMmeanEq} is by the mean inequality. 
	Inequality \eqref{eq:pfMsumXi} is because of the definition of $\bbeta_t(\delta)$ (Eq.\eqref{eq:definebeta}) and Lemma \ref{lem:SumXiEstimateInDet}. 
	And the last inequality \eqref{eq:pfMdetEst} is because estimate of $\det(\bV_t)$ by Lemma \ref{lem:detVt}.
